---
title: "My fancypants report"
author: "Sherry Khann"
date: "6/24/2021"
output: html_document
bibliography: bibliography.bib
---

```{r, include=FALSE, echo = TRUE, eval = FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE)
```

```{r, echo = FALSE}

library(dplyr)
library(ggplot2)

smoke <- c(TRUE, TRUE, TRUE, TRUE, TRUE,
           TRUE, FALSE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE, TRUE)
age <- c(35, 21, 20, 48, 20, 20, 22, 19, 19, 20, 19, 18, 24, 22, 22, 19, 21, 19, 21)
people <- data.frame(smoke, age)
people <- people %>%
  filter(age <= 34)
obs <- nrow(people)

```

# Introduction

## Background

### Smoking: is it good for you


# **Methods**

My esteemed colleagues and I surveyed `r obs` people. The average age of the participants was `r round(mean(age))` years. That is very _young_. **Right?**

# **Results!**

The below chart shows the age of the participants

```{r, echo = FALSE}
ggplot(data = people, 
       aes(x = age,
           y = smoke)) +
  geom_boxplot() 

```

# Conclusion 

Some people have smoked. Others have not. Bohat Fit Scene Boss!

# BiblioG

Lots of people smoke. Everyone knows that smoking is bad for you. And everyone knows that math is very easy. Drs probably shouldn't smoke on call. 
[@Rudd2014].
[@Peterman2005]